---
title: "Initial EDA Basic Outline"
author: "Madeline Mucciolo, Mia Iceland"
output: html_notebook
---

This is an outline for your Initial EDA. You can follow this outline, or you can modify it as you see fit. Do what works best for your project. 

## Research Question 

State your specific research question and why it is interesting. 



## Data Processing 

#### Data Intake 
```{r}
library(tidyverse)
library(rvest)
library(dplyr)
```

```{r}
sunshine <- read.csv(file = 'C:/Users/Mooch/OneDrive/Documents/PSU/sstat184/Sunshine hours for cities in the world.csv')
```
- Loading in the sunshine hours per city data.

```{r}
str(sunshine)
head(sunshine)
sample_n(sunshine, 10)
nrow(sunshine)
```
- The *sunshine* data has 392 cases of individual cities across the world and the number of sunshine hours they get for each month of the year. The data also contains the country each city resides in and the total number of hours of sunshine per year.


#### Data Wrangling 

- The original data *sunshine* is already pretty clean data and did not need much wrangling on its own, however there is data we can manipulate for later usage. 

```{r}
sunshine_seasons <-
  sunshine %>%
  mutate(Winter=Jan+Feb+Mar, Spring=Apr+May+Jun, Summer=Jul+Aug+Sep, Fall=Oct+Nov+Dec) %>%
  select(Country, City, Winter, Spring, Summer, Fall)

sunshine_seasons
```
- I created *sunshine_seasons* which contains the total number of hours for (roughly) each season. Technically seasons tend the start in the middle of a month, so I had to do come approzimation on how I split the seasons up.


## Data Visualization

#### Plot 1

Include R code to make one data visualization (I would encourage you to use 3 or more variables). Include a brief written description of what your graph shows. Is this graph helpful in answering your research question? If it is helpful, will you need to add/modify anything in this graph in the final report? 

#### Plot 2

Include R code to make one data visualization (I would encourage you to use 3 or more variables). Include a brief written description of what your graph shows. Is this graph helpful in answering your research question? If it is helpful, will you need to add/modify anything in this graph in the final report? 


## Conclusion

Include your initial intuition as to what the answer to your research question is using the data sets and visualizations you created. 